---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(cryogenic)
set.seed(1)
```

# cryogenic

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`cryogenic` is a package for freezing a function call, modifying its arguments
and then evaluating later.

This package is written for a particular use case I have in mind, and may not 
be generally applicable.  The functions are all in base R and quite small, and the
reasoning for having this in a package is *consistency* of the interface.

See [rlang](https://cran.r-project.org/package=rlang) 
for a much more comprehensive and generalisable approach.



## My Use Case

* Both the calling environment and evaluation environment are under my control.
    * I am not executing captured calls based on user input.
* Need an R package for this as I need to use this code across multiple packages
* Need eager evaluation of arguments when call is captured
* Need to be able to update any arguments
    * Need to be able to update an argument to have a value of `NULL` 
* Need to be able to set arguments to a default value if they aren't already present
* Nearly everything is in lists
* Need to be able to consistently add arbitrary `meta` information as an attribute 
  on the call
* There are probably other constraints which I'll add as I think of them

## What's in the box

* `capture_call()` to capture a call without evaluating it
* `modify_call()` to modify call arguments
* `evaluate_call()` to evaluate a call - and optionally modify the call arguments
  just prior to the evaluation.


## Installation

You can install from [GitHub](https://github.com/coolbutuseless/cryogenic) with:

``` r
# install.package('remotes')
remotes::install_github('coolbutuseless/cryogenic')
```

## Simple example 1

* capture a call 
* modify the call
* evaluate the call

```{r}
library(cryogenic)

cc <- capture_call(runif(n = 10, min=-3))
cc

cc <- modify_call(cc, defaults = list(min=0, max=5), update = list(n = 5))
cc

evaluate_call(cc)
```


## Simple example 2

* capture a call 
* simultaneously update a call and evalute it 

```{r}
library(cryogenic)

cc <- capture_call(runif(n = 10, min=-3))
cc

evaluate_call(cc, defaults = list(min=0, max=5), update = list(n = 15))
```


## Simple example 3


```{r error = TRUE}
library(cryogenic)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Capture a call as-is.
#
# * the function does not have to exist in the capturing environment
# * By default, all arguments are eagerly evaluated in the environment in which
#   the call was captured
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cc <- capture_call(farnarkle(6, x = 2, y = 3, z = 2+9, error = TRUE))
cc


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Update the arguments to the call
#
# * 'defaults' are only added to the arguments if the named argument does 
#    not already exist there.
# * 'update' values are added to the arguments unconditionally
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cc <- modify_call(
  cc, 
  defaults = list(x = NULL, y = 7), 
  update   = list(z = NULL, na.rm = TRUE),
  delete   = c('error')
)

cc


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# 'farnarkle' is not yet defined, so evaluation should fail
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
evaluate_call(cc)


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# define farnarkle and it should work
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
farnarkle <- function(...) {print("Hello #Rstats")}
evaluate_call(cc)
```


## Related Software

* `rlang` offers a lot of tools for call modification, but wasn't quite a match
for how I'm working.
* `pryr::modify_call()` is similar to what is done in this package, but `cryogenic`
offers a few more features I need.

## Acknowledgements

* R Core for developing and maintaining the language.
* CRAN maintainers, for patiently shepherding packages onto CRAN and maintaining
  the repository
